Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-03-25 doc/GMP2015/revision_2/s03_drp.tex
Started revision 2 directory. Got rid of \cutout, \addin, and \notetoreviewers macros.

\addin{
\sidenote{In this section, $G$ is always assumed to be isostatic.}
}

@@

\notetoreviewer{The following proof was moved in from the appendix.}

@@

This proof of this theorem relied on the following crucial observation and lemma that are also used for other types of qusecs in the \cutout{A}\addin{a}pplication sections (\ref{sec:bodypin} and \ref{sec:pinnedline}) of the paper.

@@

\begin{figure*}\centering%
  %
  \includegraphics[width=0.3\linewidth]{img/epsfromtikz/demo_graph_candrp_seq}
  \caption{\notetoreviewer{This is a new figure.} \addin{The sequential canonical DR-plan of $G_{\Delta}$ from Figure~\ref{fig:demo_graph:graph}, which is optimal (as explained in the proof of Theorem~\ref{theorem:algo_complexity}). The children of the triangle are omitted. Compare to to the typical canonical DR-plan shown in Figure~\ref{fig:demo_graph:candrp}. Also, note that the bottom-left node, the triangle $bce$, is the intersection of the 3 children of $G_{\Delta}$ in $ComDRP(G_{\Delta})$, shown in Figure~\ref{fig:demo_graph:comdrp}.}}
  \label{fig:demo_graph:candrpseq}
\end{figure*}%

@@

\addin{
\begin{conjecture}
\label{conj:mfaisoptimal}
    The Modified Frontier Algorithm (MFA)~\cite{lomonosov2004graph} finds a canonical, and hence optimal, DR-plan.
\end{conjecture}

The difficulty of proving Conjecture~\ref{conj:mfaisoptimal} arises from the fact that MFA is a bottom-up algorithm, involving complex datastructures. However, such a proof, even if it exists, would not be possible without the new notion of a canonical DR-plan at hand. The intuition for this conjecture comes from the similarity of the DR-plan generated by MFA to that of the sequential decomposition described in the proof of Theorem~\ref{theorem:algo_complexity}. The strength of MFA compared to other DR-planning algorithms is illustrated in the paper~\cite{lomonosov2004graph}. While MFA also offers complexity $O(n^3)$, it does not guarantee optimality.
}

>>>>

\sidenote{In this section, $G$ is always assumed to be isostatic.}

@@

@@

This proof of this theorem relied on the following crucial observation and lemma that are also used for other types of qusecs in the application sections (\ref{sec:bodypin} and \ref{sec:pinnedline}) of the paper.

@@

\begin{figure*}\centering%
  %
  \includegraphics[width=0.3\linewidth]{img/epsfromtikz/demo_graph_candrp_seq}
  \caption{The sequential canonical DR-plan of $G_{\Delta}$ from Figure~\ref{fig:demo_graph:graph}, which is optimal (as explained in the proof of Theorem~\ref{theorem:algo_complexity}). The children of the triangle are omitted. Compare to to the typical canonical DR-plan shown in Figure~\ref{fig:demo_graph:candrp}. Also, note that the bottom-left node, the triangle $bce$, is the intersection of the 3 children of $G_{\Delta}$ in $ComDRP(G_{\Delta})$, shown in Figure~\ref{fig:demo_graph:comdrp}.}
  \label{fig:demo_graph:candrpseq}
\end{figure*}%

@@

\begin{conjecture}
\label{conj:mfaisoptimal}
    The Modified Frontier Algorithm (MFA)~\cite{lomonosov2004graph} finds a canonical, and hence optimal, DR-plan.
\end{conjecture}

The difficulty of proving Conjecture~\ref{conj:mfaisoptimal} arises from the fact that MFA is a bottom-up algorithm, involving complex datastructures. However, such a proof, even if it exists, would not be possible without the new notion of a canonical DR-plan at hand. The intuition for this conjecture comes from the similarity of the DR-plan generated by MFA to that of the sequential decomposition described in the proof of Theorem~\ref{theorem:algo_complexity}. The strength of MFA compared to other DR-planning algorithms is illustrated in the paper~\cite{lomonosov2004graph}. While MFA also offers complexity $O(n^3)$, it does not guarantee optimality.

### 2015-03-25 doc/GMP2015/revision_2/s04_recombination.tex
Started revision 2 directory. Got rid of \cutout, \addin, and \notetoreviewers macros.

In the following, we formulate the problem of \dfn{optimal modification}\cutout{,} of the indecomposable algebraic system $I$ into a decomposable system with a small DR-plan (low algebraic complexity). Leveraging recent results on \dfn{Cayley configuration spaces}, our approach to the optimal modification problem achieves the following:

@@

\myexample
[Using Cayley configuration space].
A graph $G=K_{3,3}$  cannot be decomposed into any nontrivial isostatic graphs, i.e\addin{.}, its DR-plan has a root and 9 children corresponding to the 9 edges. Solving or recombining the system $(G,\delta)$ corresponding to the root of this DR-plan involves solving a quadratic system with 8 equations and variables. Instead of simultaneously solving this system, we could instead use the fact that $G=K_{3,3}$ is in OMD$_2$: remove the edges $e_1,e_2$ in Figure \ref{fig:omd_k33_example} to give a partial 2-tree $G'$. Now add the non-edges $f_1,f_2$ to give a 2-tree $H$ with a DR-plan of size 2. The Cayley configuration space $\Phi_f(G', \delta_{E\setminus e})$ is a single interval of attainable length values $\lambda_F$ for the edge $f$. When $\delta$ is generic, i.e, does not admit collinearities or coincidences in the realizations of $(G,\delta)$, the realization space of $(H, \left<\delta_{E\setminus e}, \lambda_f\right>)$ has 16 solutions $q^p_{\lambda_f}$ (modulo orientation preserving isometries), with distinct orientation types $\sigma_p$ (two orientation choices for each of the 4 triangles) that can be obtained by solving a sequence of 4 single quadratics in 1 variable (DR-plan of size 2). By subdivided binary search in the interval $\lambda_f \in \Phi_f(G', \delta_{E\setminus e})$, the desired solution $p$  of $(G,\delta)$ is found when the length of the nonedge $e$ in  the realization $q^p_{\lambda_f}$ is $\delta_e$.

@@

\subsection{Optimized Modification by Enlarging the class of Reduced
Graphs}
\label{sec:tdecomp}
%
It is possible in principle to decrease $k$ for a OMD$_k$ graph (i.e, the number of edges to be removed to ensure an isostatic completion that is decomposable with a small DR-plan) by considering reduced graphs $G'$ (and modified graphs $H$) that come from a larger class than partial 2-trees but nevertheless have convex Cayley configuration spaces at least when the realization space is restricted to a sufficiently comprehensive orientation type. In particular, the so-called \dfn{tree-decomposable graphs of low Cayley complexity} \cite{sitharam2011cayleyI,sitharam2011cayleyII} include the partial 2-trees and many others that are not partial 2-trees. See an illustration in Figure \ref{fig:omd_k33_example}. These too result in DR-plans of size 2 or 3, putting $G$ in the class OMD$_k$ and thus meeting Criteria (a) and (b). The Criterion (c) is met---for example when $k=1$---because 1-dof Cayley configuration spaces of linkages based on such graphs $G'$ are known to be single intervals when a comprehensive orientation type $\sigma_p$ of the sought solution $p$ is given. In addition, the bounds of these intervals are of low algebraic complexity. More precisely, the bounds  can themselves be computed using a DR-plan of size 2 or 3, i.e\addin{.}, the computation of these bounds is tree-decomposable. Alternatively, the bounds are in a simple quadratic or radically solvable extension field over the rationals, or can be computed by solving a triangularized system of quadratics.

>>>>

In the following, we formulate the problem of \dfn{optimal modification} of the indecomposable algebraic system $I$ into a decomposable system with a small DR-plan (low algebraic complexity). Leveraging recent results on \dfn{Cayley configuration spaces}, our approach to the optimal modification problem achieves the following:

@@

\myexample
[Using Cayley configuration space].
A graph $G=K_{3,3}$  cannot be decomposed into any nontrivial isostatic graphs, i.e., its DR-plan has a root and 9 children corresponding to the 9 edges. Solving or recombining the system $(G,\delta)$ corresponding to the root of this DR-plan involves solving a quadratic system with 8 equations and variables. Instead of simultaneously solving this system, we could instead use the fact that $G=K_{3,3}$ is in OMD$_2$: remove the edges $e_1,e_2$ in Figure \ref{fig:omd_k33_example} to give a partial 2-tree $G'$. Now add the non-edges $f_1,f_2$ to give a 2-tree $H$ with a DR-plan of size 2. The Cayley configuration space $\Phi_f(G', \delta_{E\setminus e})$ is a single interval of attainable length values $\lambda_F$ for the edge $f$. When $\delta$ is generic, i.e, does not admit collinearities or coincidences in the realizations of $(G,\delta)$, the realization space of $(H, \left<\delta_{E\setminus e}, \lambda_f\right>)$ has 16 solutions $q^p_{\lambda_f}$ (modulo orientation preserving isometries), with distinct orientation types $\sigma_p$ (two orientation choices for each of the 4 triangles) that can be obtained by solving a sequence of 4 single quadratics in 1 variable (DR-plan of size 2). By subdivided binary search in the interval $\lambda_f \in \Phi_f(G', \delta_{E\setminus e})$, the desired solution $p$  of $(G,\delta)$ is found when the length of the nonedge $e$ in  the realization $q^p_{\lambda_f}$ is $\delta_e$.

@@

\subsection{Optimized Modification by Enlarging the class of Reduced
Graphs}
\label{sec:tdecomp}
%
It is possible in principle to decrease $k$ for a OMD$_k$ graph (i.e, the number of edges to be removed to ensure an isostatic completion that is decomposable with a small DR-plan) by considering reduced graphs $G'$ (and modified graphs $H$) that come from a larger class than partial 2-trees but nevertheless have convex Cayley configuration spaces at least when the realization space is restricted to a sufficiently comprehensive orientation type. In particular, the so-called \dfn{tree-decomposable graphs of low Cayley complexity} \cite{sitharam2011cayleyI,sitharam2011cayleyII} include the partial 2-trees and many others that are not partial 2-trees. See an illustration in Figure \ref{fig:omd_k33_example}. These too result in DR-plans of size 2 or 3, putting $G$ in the class OMD$_k$ and thus meeting Criteria (a) and (b). The Criterion (c) is met---for example when $k=1$---because 1-dof Cayley configuration spaces of linkages based on such graphs $G'$ are known to be single intervals when a comprehensive orientation type $\sigma_p$ of the sought solution $p$ is given. In addition, the bounds of these intervals are of low algebraic complexity. More precisely, the bounds  can themselves be computed using a DR-plan of size 2 or 3, i.e., the computation of these bounds is tree-decomposable. Alternatively, the bounds are in a simple quadratic or radically solvable extension field over the rationals, or can be computed by solving a triangularized system of quadratics.

### 2015-03-25 doc/GMP2015/revision_2/s05_problems.tex
Started revision 2 directory. Got rid of \cutout, \addin, and \notetoreviewers macros.

In this section we provide a unified view of the various problems studied in the previous 2 sections, along with formal reductions between them\cutout{, and}\addin{. We discuss their} relationship\cutout{s} to other known problems and results as well as open questions.

@@

In the recombination setting, the corresponding \dfn{restricted OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction} or to be a low Cayley complexity tree-decomposable graph as in Section \ref{sec:tdecomp}. Clearly these problems have deterministic polynomial time algorithms \addin{in $n$}, \addin{but} the algorithms run in time exponential in $k$.

>>>>

In this section we provide a unified view of the various problems studied in the previous 2 sections, along with formal reductions between them. We discuss their relationship to other known problems and results as well as open questions.

@@

In the recombination setting, the corresponding \dfn{restricted OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction} or to be a low Cayley complexity tree-decomposable graph as in Section \ref{sec:tdecomp}. Clearly these problems have deterministic polynomial time algorithms in $n$, but the algorithms run in time exponential in $k$.

### 2015-03-25 doc/GMP2015/revision_2/s06_problempinning.tex
Started revision 2 directory. Got rid of \cutout, \addin, and \notetoreviewers macros.

\notetoreviewer{Changed section title from ``Application: Finding completions of underconstrained glassy structures to isostatic''}
% \bibliography{paper}

@@

In all cases, we are specifically interested in how to add additional constraints \addin{such that} the resulting isostatic structure \cutout{with} \addin{has} a small DR-plan\cutout{, so} \addin{; this way} a realization can be found\addin{, allowing efficient} \cutout{and} stress and other property design\cutout{ can be efficient}. To answer these questions, we first introduce the qusecs that are used to model these materials. We will discuss \cutout{Item 2} \addin{item (2)} in detail in this section.

@@

    Such a body-pin graph\addin{, $G_{BP}$,} can also be seen as a \dfn{body-bar graph}\addin{, $G_{BB}$,} where the bodies \addin{of $G_{BB}$} are the original bodies \addin{of $G_{BP}$} and each pin \cutout{represents 2 bars from one body to another} \addin{between bodies in $G_{BP}$ are replaced with 2 bars in $G_{BB}$ between the same bodies}.
    Such body-bar graphs with 1 and 2-dof can be characterized by being $(3,4)$ and $(3,5)$-tight respectively \cite{Lee:2007:PGA} \cite{streinu2009sparse} (defined in \ref{sec:appendix:defs}). \addin{See Figure \ref{fig:bodypindrp:b}.}
\end{definition}

@@

\begin{definition}
    A \dfn{$(k,l)$-tight DR-plan} is one in which each child node is either a vertex maximal proper $(k,l)$-tight sub-graph of the parent node or it is trivial. In our case, the trivial nodes are \cutout{just} the bodies.
\end{definition}

@@

The strong Church-Rosser property holds\addin{,} making all canonical DR-plans optimal:
%
\begin{remark}\label{rem:1dofcanon}
    When the input is independent, all $(3,4)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$-tight case for bar-joint graphs discussed in Section \ref{sec:DRP}. This is because such $(3,4)$-tight graphs are matroidal and have a pebble game\cutout{, shown in} \cite{Lee:2007:PGA}.
\end{remark}

@@

The above discussion leads to the main theorem:
\begin{theorem*}
\label{thm:1dofcase}
    Given a 1-dof body-pin or triangle-multipin graph \cutout{$G$} and corresponding 1-dof DR-plan \cutout{$T$}, there is a quadratic algorithm for the 1-dof optimal completion problem of Section \ref{sec:recomb}.
\end{theorem*}

>>>>

% \bibliography{paper}

@@

In all cases, we are specifically interested in how to add additional constraints such that the resulting isostatic structure has a small DR-plan; this way a realization can be found, allowing efficient stress and other property design. To answer these questions, we first introduce the qusecs that are used to model these materials. We will discuss item (2) in detail in this section.

@@

    Such a body-pin graph, $G_{BP}$, can also be seen as a \dfn{body-bar graph}, $G_{BB}$, where the bodies of $G_{BB}$ are the original bodies of $G_{BP}$ and each pin between bodies in $G_{BP}$ are replaced with 2 bars in $G_{BB}$ between the same bodies.
    Such body-bar graphs with 1 and 2-dof can be characterized by being $(3,4)$ and $(3,5)$-tight respectively \cite{Lee:2007:PGA} \cite{streinu2009sparse} (defined in \ref{sec:appendix:defs}). See Figure \ref{fig:bodypindrp:b}.
\end{definition}

@@

\begin{definition}
    A \dfn{$(k,l)$-tight DR-plan} is one in which each child node is either a vertex maximal proper $(k,l)$-tight sub-graph of the parent node or it is trivial. In our case, the trivial nodes are the bodies.
\end{definition}

@@

The strong Church-Rosser property holds, making all canonical DR-plans optimal:
%
\begin{remark}\label{rem:1dofcanon}
    When the input is independent, all $(3,4)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$-tight case for bar-joint graphs discussed in Section \ref{sec:DRP}. This is because such $(3,4)$-tight graphs are matroidal and have a pebble game \cite{Lee:2007:PGA}.
\end{remark}

@@

The above discussion leads to the main theorem:
\begin{theorem*}
\label{thm:1dofcase}
    Given a 1-dof body-pin or triangle-multipin graph and corresponding 1-dof DR-plan, there is a quadratic algorithm for the 1-dof optimal completion problem of Section \ref{sec:recomb}.
\end{theorem*}

### 2015-03-25 doc/GMP2015/revision_2/s07_pinnedline.tex
Started revision 2 directory. Got rid of \cutout, \addin, and \notetoreviewers macros.

The canonical DR-plan of Section \ref{sec:DRP} can also be applied to analyze and solve the structure of
\cutout{cross-linking collagen and cellulose microfibrils in animal and plant cell walls, and actin filaments in the cytoskeleton}
\addin{cross-linking collagen microfibrils in animals, cellulose microfibrils in plant cell walls, and actin filaments in the cytoskeleton}
by modeling these structures as \dfn{pinned line-incidence systems}.

@@

\begin{figure}\centering%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/AFM_Innventia_nanocellulose}
    \caption{}\label{fig:cellulose}
\end{subfigure}\hfill%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/crosslink}
    \caption{}\label{fig:crosslink}
\end{subfigure}\hfill%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/pinned}
    \caption{}
    \label{fig:pinned_line}
\end{subfigure}%
\caption{\notetoreviewer{Combined 2 figures.} (\ref{fig:cellulose}) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. \ref{fig:crosslink} Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}. \ref{fig:pinned_line} An isostatic pinned line-incidence graph\addin{, representing fibrils and their attachments.}}
\end{figure}%

@@

Theorem~\ref{theorem:main} holds for pinned line-incidence graphs with \cutout{the above} \addin{this} modified definition. The proof is similar to the original proof (in Section~\ref{sec:DRP}) using the same set of lemmas and
%
%\begin{corollary}\label{cor:pinned}
%Given a isostatic pinned line-incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
%\begin{enumerate}
%    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$.
%    \item if $C_i \cap C_j$ is isostatic then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
%\end{enumerate}
%\end{corollary}
%
the following modified version of Observation~\ref{lemma:union_intersection},
% observation, which
%serves a similar function to Observation~\ref{lemma:union_intersection} in Section~\ref{sec:DRP}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
which  can be proved using a simple counting based argument.

@@

Given \cutout{Lemma} \addin{Observation}~\ref{lem:pinned_union_intersection}, % and the modified definition of DR-plan,
Lemma \addin{\ref{lemma:combined_lemma}, Point} \ref{lemma:wc_intersection_is_C} and \ref{lemma:uc_intersection_makes_all_uc}\addin{,} straightforwardly extend to pinned line-incidence graphs. The proof of Point~\ref{lemma:wc_intersection_makes_all_wc} for pinned line-incidence graphs is given in~\ref{sec:appendix_pinned}.
%The following lemma serves as Lemma~ for pinned line-incidence and can be proved similarly.
%\begin{lemma}
%\label{lem:vertex_intersection}
%If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
%\end{lemma}
%Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lemma:uc_intersection_makes_all_uc},
Thus it is straightforward to adapt the proof of Theorem~\ref{theorem:main} to  pinned line-incidence graphs.
%thus proving Corollary~\ref{cor:pinned}.
%
Consequently, we can efficiently find the optimal DR-plan for  pinned line-incidence graphs using basically the same algorithm as for  bar-joint graphs.

>>>>

The canonical DR-plan of Section \ref{sec:DRP} can also be applied to analyze and solve the structure of cross-linking collagen microfibrils in animals, cellulose microfibrils in plant cell walls, and actin filaments in the cytoskeleton by modeling these structures as \dfn{pinned line-incidence systems}.

@@

\begin{figure}\centering%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/AFM_Innventia_nanocellulose}
    \caption{}\label{fig:cellulose}
\end{subfigure}\hfill%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/crosslink}
    \caption{}\label{fig:crosslink}
\end{subfigure}\hfill%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/pinned}
    \caption{}
    \label{fig:pinned_line}
\end{subfigure}%
\caption{(\ref{fig:cellulose}) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. \ref{fig:crosslink} Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}. \ref{fig:pinned_line} An isostatic pinned line-incidence graph, representing fibrils and their attachments.}
\end{figure}%

@@

Theorem~\ref{theorem:main} holds for pinned line-incidence graphs with this modified definition. The proof is similar to the original proof (in Section~\ref{sec:DRP}) using the same set of lemmas and
%
%\begin{corollary}\label{cor:pinned}
%Given a isostatic pinned line-incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
%\begin{enumerate}
%    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$.
%    \item if $C_i \cap C_j$ is isostatic then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
%\end{enumerate}
%\end{corollary}
%
the following modified version of Observation~\ref{lemma:union_intersection},
% observation, which
%serves a similar function to Observation~\ref{lemma:union_intersection} in Section~\ref{sec:DRP}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
which  can be proved using a simple counting based argument.

@@

Given Observation~\ref{lem:pinned_union_intersection}, % and the modified definition of DR-plan,
Lemma \ref{lemma:combined_lemma}, Point \ref{lemma:wc_intersection_is_C} and \ref{lemma:uc_intersection_makes_all_uc}, straightforwardly extend to pinned line-incidence graphs. The proof of Point~\ref{lemma:wc_intersection_makes_all_wc} for pinned line-incidence graphs is given in~\ref{sec:appendix_pinned}.
%The following lemma serves as Lemma~ for pinned line-incidence and can be proved similarly.
%\begin{lemma}
%\label{lem:vertex_intersection}
%If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
%\end{lemma}
%Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lemma:uc_intersection_makes_all_uc},
Thus it is straightforward to adapt the proof of Theorem~\ref{theorem:main} to  pinned line-incidence graphs.
%thus proving Corollary~\ref{cor:pinned}.
%
Consequently, we can efficiently find the optimal DR-plan for  pinned line-incidence graphs using basically the same algorithm as for  bar-joint graphs.

### 2015-03-25 doc/GMP2015/revision_2/s08_conclusion.tex
Started revision 2 directory. Got rid of \cutout, \addin, and \notetoreviewers macros.

We have clarified the main source of complexity for the optimal DR-plan and recombination problems. For the former problem, when there are no overconstraints\cutout{,} (as is the case for 2D qusecs whose realizations are many common types of layered materials), we defined a canonical DR-plan and showed that \cutout{such} \addin{any} canonical DR-plan\cutout{s are} \addin{is} guaranteed to be optimal, \addin{which is} a strong Church-Rosser property\addin{. This gives} \cutout{giving} an efficient (\candrpcomplexity) algorithm to find an optimal DR-plan that satisfies other desirable characteristics.

@@

\notetoreviewer{The following section was moved in from the appendix.}

@@

\begin{openproblem}
    For fixed $k$ we have polynomial time optimal DR-planning \addin{(Section~\ref{sec:DRP})}, recombination (modification) in the presence of $k$ overconstraints\cutout{ (Section X}, optimal modification for decomposition {\sl OMD}$_k(G)$, when at most $k$ constraints are removed \addin{(Section~\ref{sec:recomb})} and also optimal completion using at most $k\le 2$ constraints in the body-pin and triangle-multipin cases under a modified measure for optimizing the DR-plan \addin{(Section~\ref{sec:table})}. However, \addin{in the running time of all of these algorithms,} $k$ appears in the exponent\cutout{ for the straightforward algorithms for these problems}.
\end{openproblem}

>>>>

We have clarified the main source of complexity for the optimal DR-plan and recombination problems. For the former problem, when there are no overconstraints (as is the case for 2D qusecs whose realizations are many common types of layered materials), we defined a canonical DR-plan and showed that any canonical DR-plan is guaranteed to be optimal, which is a strong Church-Rosser property. This gives an efficient (\candrpcomplexity) algorithm to find an optimal DR-plan that satisfies other desirable characteristics.

@@

@@

\begin{openproblem}
    For fixed $k$ we have polynomial time optimal DR-planning (Section~\ref{sec:DRP}), recombination (modification) in the presence of $k$ overconstraints, optimal modification for decomposition {\sl OMD}$_k(G)$, when at most $k$ constraints are removed (Section~\ref{sec:recomb}) and also optimal completion using at most $k\le 2$ constraints in the body-pin and triangle-multipin cases under a modified measure for optimizing the DR-plan (Section~\ref{sec:table}). However, in the running time of all of these algorithms, $k$ appears in the exponent.
\end{openproblem}
